Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2019-10-29 manuscript/manuscript.Rmd
Added interpretations to second set of questions

Conjoint analysis shows which components of a choice hold the most weight. Conjoint analysis has been widely used within social sciences to explain causality and has recently begun to be used in political and public policy fields. Helfer (2016) and Mummolo (2016) both used conjoint analysis to assess consumer perceptions of political communications. Conjoint is key in political research because it captures multidimensional causal relations.

Knudsen and Johannesson (2018) argue that political communication research requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgement of credibility. Public policy research would benefit from conjoint analysis for the same reasons.

@@

The following plots zoom in on the strength of the effects of these characteristics.

Compared to when an NGO has a friendly relationship with the host government, donors who see that an NGO faces general legal trouble abroad are less likely to donate.

@@

    - Traveled Internationally: No
      ![](output/figures/traveled.png)

    - Medium to follow news: Online (excluding social media) with all attributes
      ![](output/figures/following-news.png)

    - Medium to follow news: Online (excluding social media) with organization
      ![](output/figures/following-news2.png)

@@

![](output/figures/political-ideology.png)

@@

![](output/figures/social-views.png)
      - Religiosity
  ![](output/figures/religion.png)

@@

![](output/figures/charity-and-voluntarism.png)  
      - Association membership
  ![](output/figures/other-organizations.png)

@@

  ![](output/figures/demographics.png)
      - Gender
  ![](output/figures/gender.png)  
      - Marital Status
  ![](output/figures/marital-status.png)  
      - Education
  ![](output/figures/education.png)
      - Income
  ![](output/figures/income.png)
      - Race 
    ![](output/figures/race.png)
      - Age 
  ![](output/figures/age.png)

@@

  ![](output/figures/public-political.png)

@@

![](output/figures/public-political-social.png)

>>>>

Conjoint analysis forces a consumer to choose between alternatives, revealing which components of a choice are the most important to that consumer. Conjoint analysis has been widely used within social sciences to explain causality and has recently begun to be used in political and public policy fields. Helfer (2016) and Mummolo (2016) both used conjoint analysis to assess consumer perceptions of political communications. Conjoint is key in political research because it captures multidimensional causal relations.

Knudsen and Johannesson (2018) argue that political communication research requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgment of credibility. Because we also want to capture the complexity of a respondent's judgment of whether they should donate to an NGO or not, we used conjoint analysis to draw our conclusions.

@@

The following plots zoom in on the strength and direction of the effects of these characteristics.

Compared to when an NGO has a friendly relationship with the host government, donors who see that an NGO faces general legal trouble abroad (under crackdown or criticized) are less likely to donate.

@@

Those that haven't traveled internationally are significantly less likely to donate to NGOs than those who have.
![](output/figures/traveled.png)

Of all media sources, those that follow the news through an app or email newsletter are more likely to donate in general. Interestingly, those that read newsletters are the most likely to donate overall. They feel most comfortable donating to environmental causes. They care significantly less about managerial practices and funding sources than other groups. 
      ![](output/figures/following-news.png)

When it comes to donating to organizations, those whose top news medium is online sources (excluding social media) are least likely to donate.
![](output/figures/following-news2.png)

@@

Those that are conservative are significantly more likely to donate to the Red Cross.
![](output/figures/political-ideology.png)

@@

![](output/figures/social-views.png)

Hindus are very unlikely to donate to human rights or refugee relief, whereas Muslims are very likely to donate to human rights and refugee relief. Muslims are also very willing to donate to organizations that are facing government criticism or crackdown in the country. 
  ![](output/figures/religion.png)

@@

Those that have a history of either family or personal activism are most likely to donate to organizations. Those that haven't volunteered in the past 12 months are also more likely to donate.   
![](output/figures/charity-and-voluntarism.png)  
Those that are in a professional or humanitarian organization are most likely to donate. It's odd that those that belong to an environmental organization are less likely to donate to environmental NGOs.
  ![](output/figures/other-organizations.png)

@@

Demographics are broken down further and analyzed below.
  ![](output/figures/demographics.png)
Note: not sure if "other" indicates "male" or if male is the intercept everything else is compared to.
  ![](output/figures/gender.png)  
Overall, those that are widowed are less likely to donate to organizations than others. They also don't pay attention to financial transparency and accountability, though those that have never married do.
  ![](output/figures/marital-status.png)  
Financial transparency was important to everyone regardless of education level. 
  ![](output/figures/education.png)
Income doesn't impact the various attributes except when it comes to organization. There is a lot more spread when it comes to choosing an organization.
  ![](output/figures/income.png)
Not seeing obvious patterns across races.
    ![](output/figures/race.png)
  Across all ages, people are most likely to donate to emergency response efforts more than any other issue area. 
  ![](output/figures/age.png)

@@

Those that read printed news are least likely to donate to any of these organizations. Those that follow international news multiple times are day are more likely to donate and are less concerned when an organization is criticized by the government.  
![](output/figures/public-political.png)

@@

For the most part, these plots have too much information to gain useful insight.
![](output/figures/public-political-social.png)
